---
title: "Biden Polling"
author: "Faisal Jan"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(tidymodels)
library(broom)
library(easystats)
library(gt)
library(marginaleffects)

poll_data <- tibble(biden = as.factor(c(rep("Yes", 655), rep("No", 904)))) |>
  slice_sample(prop = 1)
```

```{r}
#| cache: true
fit_biden <- logistic_reg() |> 
    fit(biden ~ 1, data = poll_data)
```

```{r}
avg_predictions(fit_biden, type = "prob") |>
    filter(group == 'Yes') |>
    ggplot(aes(x = 1, y = estimate, ymin = conf.low, ymax = conf.high)) +
    geom_pointrange(size = 1.2, color = "#212121") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     breaks = seq(0.38, 0.46, by = 0.02),
                     limits = c(0.37, 0.47)) + # Adjust y-axis limits and breaks
  labs(
    title = "Support for President Biden in March 2024",
    subtitle = "42% is not a good sign for an incumbent seeking reelection",
    caption = "Source: YouGov poll, March 2024.",
    y = "Probability"
  ) +
  theme_minimal() + # Use a minimal theme
  theme(
    axis.title.x = element_blank(), # Remove x-axis title
    axis.text.x = element_blank(), # Remove x-axis text/labels
    axis.ticks.x = element_blank(), # Remove x-axis ticks
    panel.grid.major.x = element_blank(), # Remove major x-axis grid lines
    panel.grid.minor.x = element_blank(), # Remove minor x-axis grid lines
    panel.grid.minor.y = element_blank(), # Remove minor y-axis grid lines
    plot.title = element_text(hjust = 0, size = 16, face = "bold"), # Left-align and style title
    plot.subtitle = element_text(hjust = 0, size = 14), # Left-align and style subtitle
    plot.caption = element_text(hjust = 1, size = 10) # Right-align and style caption
  )
```

U.S Elections are more about a competition between Republication and Democratic parties than general elections. Using the data of voters in the 2024 U.S. presidential election, I seek to predict what proportion of all votes will be cast for Joe Biden in November election. While samples containing some certain groups by age or region than their share of the population, create a representativeness gap. I model Biden support, a binary outcome variable to express whether a voter voted Biden or not, as a logistic function with no covariates, capturing the overall proportion of support in the population. The outcome values ‘Yes’ means respondent supports Biden and ‘No’ for non-supporters. We estimate that around 42% are will support Joe Biden in November election, with a 95% confidence interval ranging from 40% to 45%.

$$
\text{logit}(\Pr(Y = 1 \mid X_1, X_2, \dots, X_k)) = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_k X_k
$$

$$
\hat{Y} = \text{logit}^{-1}(-0.32) = \frac{1}{1 + e^{0.32}} \approx 0.42
$$

```{r}
# Create a nicely formatted table
fit_biden |> tidy(conf.int = TRUE) |>
  gt() |>
  fmt_number(
    columns = c(estimate, std.error, statistic, conf.low, conf.high),
    decimals = 2
  ) |>
  fmt_scientific(
    columns = p.value,
    decimals = 2
  ) |>
  cols_label(
    term = "Term",
    estimate = "Estimate",
    std.error = "Std. Error",
    statistic = "Z-value",
    p.value = "P-value",
    conf.low = "Conf. Low",
    conf.high = "Conf. High"
  ) |>
  tab_header(
    title = "Logistic Regression Model Summary"
  )
```
